{\Huge Supersymmetry} \\ \vspace{5mm} Lecture notes for FYS5190/FYS9190 Supersymmetry

### 2023-10-03 superspace.tex
Updates to 3.3 and 3.4

If we now want to see how a Lorentz transformation $\Lambda$ acts for example on a scalar function $F(x)$ -- this could be a scalar quantum field -- we can write $F(x)=\exp(ix^\mu P_\mu)F(0)$. This means that the transformation is essentially captured as $x'$ in $\Lambda\exp(ix^\mu P_\mu)= \exp(ix'^\mu P_\mu)$. Now, from the above we have
\[ \Lambda\exp(ix^\mu P_\mu)=\Lambda T(x)=T(\Lambda x) \Lambda, \]
and since the Lorentz transformation does nothing to a scalar coordinate independent quantity such as $F(0)$, we have $x'^\mu=\Lambda^\mu_{~\nu} x^\nu$, and the scalar function transforms the way we are used to under Lorentz transformations, namely $\Lambda F(x)= F(x')$. This argument can easily be extended to vector fields $A_\mu(x)$ and higher rank tensors, for example
\[ \Lambda A^\nu(x)= \Lambda^\mu_{~\nu} A^\nu(x'). \]
 The way we have defined four-vectors have built the Lorentz transformations of Special Relativity into our equations.

@@

In order for the exponential map to make sense the parameters $\theta$ need to anti-commute just like the $Q$s so that the contractions $\theta^{A} Q_A$ and $\bar{\theta}_{\dot{A}}\bar{Q}^{\dot{A}}$ follow ordinary commutation rules. Otherwise the commutation properties of the exponential map would be different order by order.
 As physicists we also want to know the dimensions of our new parameters. To do this we first look at Eq.~(\ref{eq:QQbarweyl}):
\[\{Q_A, \bar{Q}_{\dot{B}}\} = 2\sigma^{\mu}_{A\dot{B}}P_\mu,\]
where we know that $P_\mu$ has mass dimension $[P_\mu] = M$. This means that $[Q^2] = M$ and $[Q]=M^{1/2}$. In the exponential, all terms must have mass dimension zero to make sense. This means that $[\theta Q] = 0$, and therefore $[\theta] = M^{-1/2}$.

We now want to find the effect of supersymmetry transformations (transformations by the super-Poincaré group) on the superspace coordinates, and we begin by noting that any $SP$ transformation can effectively be written in the following way without the boosts and rotations of the Lorentz group:
\[g_0(a,\alpha) = \exp[ia^\mu P_\mu + i\alpha^AQ_A +i\bar{\alpha}^{\dot{A}}\bar{Q}_{\dot{A}}],\]
effectively setting $\omega_{\rho\nu}=0$, because we can again show that\footnote{Fortunately we are not going to do this because it is messy, but it can be done using the algebra of the group and the series expansion of the exponential function. Note, however, that the proof rests on the $P$s and $Q$s forming a closed set, which we saw in the algebra Eqs.~(\ref{eq:QPweyl})--(\ref{eq:QQbarweyl}).}
\begin{equation}
\exp\left[\frac{i}{2}\omega_{\rho\nu}M^{\rho\nu}\right]g_0(a,\alpha) = g_0(\Lambda a,S(\Lambda)\alpha)\exp\left[\frac{i}{2}\omega_{\rho\nu}M^{\rho\nu}\right],
\end{equation}
{\it i.e.}\ that all that a Lorentz boost does is to transform spacetime coordinates by $\Lambda$ and Weyl spinors by $S(\Lambda)$, which is the spinor representation of $\Lambda$ ($SL(2,\mathbb C)$). Thus, in more colloquial terms, for the supersymmetry transformation it does not matter which reference frame we are working in, we know how the transformation changes between the frames, given by  $\Lambda a$  and $S(\Lambda)\alpha$.

@@

Now we take a closer look at the commutator:\footnote{Using that $P_\mu$ commutes with all elements in the  algebra, as well as $[\theta^A Q_A, \xi^B Q_B] = -\theta^A\xi^B\{Q_A, Q_B\} = 0$, and the same for $\bar{Q}^{\dot{B}}$.}

@@

As a crucial by-product we can now write down a differential representation for the supersymmetry generators by applying the standard expression for the generators $X_i$ of a Lie algebra, given the composition functions $f_\pi$:
\[ iX_j = \frac{\partial f_\pi}{\partial a_j}\frac{\partial}{\partial z_\pi},\]
which gives us:
\begin{eqnarray}
iP_\mu &=& \partial_\mu \label{eq:diffrepP},\\
iQ_A &=& -i(\sigma^\mu\bar{\theta})_A\partial_\mu +\partial_A,\\
i\bar{Q}^{\dot{A}} &=& -i(\bar{\sigma}^\mu \theta)^{\dot{A}}\partial_\mu +\partial^{\dot{A}}.
\label{eq:diffrepQbar}
\end{eqnarray}

%%%%%%%%%%%%%%%
\section{Superspace calculus}
\label{app:calc}
%%%%%%%%%%%%%%%
Grassmann numbers $\theta$ are numbers that anti-commute with each other but not with ordinary numbers. We will here use four such numbers and in addition we want to place them in Weyl spinors, indexed by $A$ and $\dot{A}$:\footnote{We can already see how this can be useful: if we consistently use $\theta^AQ_A$ and $\bar{\theta}_{\dot{A}}\bar{Q}^{\dot{A}}$ instead of only $Q_A$ and $\bar{Q}^{\dot{A}}$ in Eqs.~(\ref{eq:QPweyl})--(\ref{eq:QQbarweyl}) we can actually rewrite the superalgebra as an ordinary Lie algebra, but with Grassman elements, because of these commutation properties.}
\[\{\theta^A, \theta^B\} = \{\theta^A, \bar{\theta}^{\dot{B}}\} = \{ \bar{\theta}^{\dot{A}}, \theta^B\} = \{\bar{\theta}^{\dot{A}}, \bar{\theta}^{\dot{B}}\} =0.\]
From this we get the relationships:\footnote{There is no summation implied in the first line. These are of course the same relations we already used for the Weyl spinors.}
\begin{eqnarray}
\theta_A^2 &=& \theta_A \theta_A = -\theta_A \theta_A = 0, \label{eq:thetasq}\\
\theta^2 &\equiv& \theta\theta \equiv \theta^A\theta_A = -2\theta_1\theta_2,\\
\bar{\theta}^2 &\equiv& \bar{\theta}\bar{\theta} \equiv \bar{\theta}_{\dot{A}}\bar{\theta}^{\dot{A}} = 2\bar{\theta}^{\dot{1}}\bar{\theta}^{\dot{2}}.
\end{eqnarray}
Notice that if we have a function $f$ of a Grassman number, say $\theta_A$, then the all-order expansion of that function in terms of $\theta_A$, is
\begin{equation}
f(\theta_A) = a_0 + a_1 \theta_A,\label{eq:fexp}
\end{equation}
as there are simply no more terms because of (\ref{eq:thetasq}).

We now need to define differentiation and integration on these numbers in order to create a calculus for them.\footnote{These definitions have no infinitesimal interpretations, not is there any notion of definite integrals.}
\df{We define differentiation by:
\[\partial_A \theta^B \equiv \frac{\partial}{\partial \theta^A} \theta^B \equiv \delta_A{}^B,\]
with a product rule
\begin{eqnarray}
\partial_A(\theta^{B_1} \theta^{B_2}\theta^{B_3}\ldots\theta^{B_n} ) &\equiv& (\partial_A\theta^{B_1}) \theta^{B_2}\theta^{B_3}\ldots\theta^{B_n}\nonumber\\
&&- \theta^{B_1}(\partial_A\theta^{B_2})\theta^{B_3}\ldots\theta^{B_n}\nonumber\\
 && +\ldots+(-1)^{n-1}\theta^{B_1}\theta^{B_2}\ldots(\partial_A\theta^{B_n}).
 \end{eqnarray}}
 This implies that the differential operator $\partial_A$ is itself a Grassmann number and anti-commutes. We can show that the indices of these operators can be raised and lowered with the $\epsilon$ in Eqs.~(\ref{eq:epsilonAB}) and (\ref{eq:epsilonAdotBdot}).

\df{The integral of a function $f$ of a Grassmann number $\theta_A$ is defined as a functional $I[f]$
\[ I[f]=\int d\theta_A f(\theta_A), \]
which evaluates to a $c$-number. The evaluation is defined by the relations
 \[\int d\theta_A \equiv 0,\quad \int d\theta_A \theta_A \equiv 1,\] 
and similarly for $\bar\theta_{\dot A}$, and we demand linearity:
\[\int d\theta_A[af(\theta_A) + bg(\theta_A)] \equiv a\int d\theta_A f(\theta_A) + b\int d\theta_A g(\theta_A).\]
In these definitions there is no implied summation over the index $A$.}

This has one surprising property. If we take the integral of (\ref{eq:fexp}) we get:
\[\int d\theta_A f(\theta_A) = a_1 = \partial^A f(\theta_A),\]
meaning that differentiation and integration has the same effect on Grassman numbers.

To integrate over multiple Grassman numbers we define volume elements as
\df{
\[d^2\theta \equiv -\frac{1}{4}d\theta^Ad\theta_A,\]
\[d^2\bar{\theta} \equiv -\frac{1}{4}d\bar{\theta}_{\dot{A}}d\bar{\theta}^{\dot{A}},\]
\[d^4\theta \equiv d^2\theta d^2\bar{\theta}.\]}
and we demand that the integral operators anti-commute, just as the differential operators
\[ \{\int d\theta_A,\int d\theta_B\}=\{\int d\theta_A,\theta_B\}=0.\]

This specific volume element definition is made to normalise the following integrals
\[\int d^2\theta\text{ }\theta\theta = 1,\]
\[\int d^2\bar{\theta}\text{ }\bar{\theta} \bar{\theta} = 1,\]
\[\int d^4 \theta \text{ }(\theta\theta)(\bar{\theta} \bar{\theta}) = 1.\]

@@

%%%%%%%%%%%%%%%
\section{Covariant derivatives}
\label{sec:covder}
%%%%%%%%%%%%%%%
Similar to the properties of covariant derivatives for gauge transformations in gauge theories, it would be nice to have a derivative that is invariant under supersymmetry transformations, {\it i.e.}\ commutes with supersymmetry operators. Obviously $P_\mu = -i\partial_\mu$ does this, but more general covariant derivatives can be made.
\df{The following {\bf covariant derivatives} commute with supersymmetry transformations:
\begin{eqnarray}
D_A &\equiv& \partial_A + i(\sigma^\mu\bar{\theta})_A\partial_\mu ,\\
\bar{D}_{\dot{A}} &\equiv& -\partial_{\dot{A}}-i(\theta\sigma^\mu)_{\dot{A}}\partial_\mu.
\end{eqnarray}}

@@

%From the covariant derivatives we can construct projection operators.
%\df{The operators
%\begin{eqnarray}
%\pi_+ &\equiv& -\frac{1}{16\Box} \bar{D}^2D^2,\\
%\pi_- &\equiv& -\frac{1}{16\Box} D^2\bar{D}^2,\\
%\pi_T &\equiv& \frac{1}{8\Box} \bar{D}_{\dot{A}}D^2\bar{D}^{\dot{A}},
%\end{eqnarray}
%with $\Box\equiv\partial_\mu\partial^\mu$, are projection operators, {\it i.e.}\ they fulfil:
%\begin{eqnarray}
%\pi_{\pm,T}^2 &=&\pi_{\pm, T} \\
%\pi_+\pi_- &=& \pi_+\pi_T = \pi_-\pi_T= 0\\
%1&=&\pi_+ + \pi_- + \pi_T
%\end{eqnarray}
%}

@@

We can expand any such superfield $\Phi(x, \theta, \bar{\theta})$  as a power series in $\theta$ and $\bar{\theta}$. This gives, in general,
%\footnote{Equation (\ref{eq:gen_sup}) can be shown to be closed under supersymmetry transformations, meaning that a superfield transforms into another superfield under the transformations of the previous section.}
\begin{eqnarray}
\Phi(x, \theta, \bar{\theta}) &=& f(x) + \theta^A\phi_A(x) + \bar{\theta}_{\dot{A}}\bar{\chi}^{\dot{A}}(x) + \theta\theta m(x) + \bar{\theta}\bar{\theta}n(x) \nonumber\\ 
&& + \theta \sigma^\mu \bar{\theta}V_\mu(x) + \theta \theta \bar{\theta}_{\dot{A}}\bar{\lambda}^{\dot{A}}(x) +\bar{\theta}\bar{\theta}\theta^A\psi_A(x) + \theta\theta\bar{\theta}\bar{\theta}d(x),\label{eq:gen_sup}
\end{eqnarray} 
where the functions of space-time coordinates $x$ are called the {\bf component fields}. Any superfield without explicit spinor indices, such as the one above, commutes with any other superfield, because all the Grassmann numbers appear in contracted pairs.

The properties of the component fields can be deduced from the requirement that $\Phi$ must be an (operator valued) Lorentz scalar or pseudoscalar. This is shown in Table~\ref{tab:gensup} along with the corresponding degrees of freedom each field has.
\begin{center}
   \begin{tabular}{c |l| c} 
   \noalign{\smallskip}\hline\noalign{\smallskip}
   {\bf Component field} & {\bf Type} & {\bf d.o.f.} \\
   \noalign{\smallskip}\hline\noalign{\smallskip}
   $f(x)$, $m(x)$, $n(x)$ & Complex (pseudo) scalar & 2\\
   $\psi_A(x)$, $\phi_A(x)$ & Left-handed Weyl spinor & 4\\
   $\bar{\chi}^{\dot{A}}(x)$, $\bar{\lambda}^{\dot{A}}(x)$ &Right-handed Weyl spinor& 4\\
   $V_\mu(x)$ & Lorentz 4-vector (complex) & 8\\
   $d(x)$ & Complex scalar & 2 \\
   \noalign{\smallskip}\hline\noalign{\smallskip}
    \end{tabular}
   \captionof{table}{Field content of a general superfield. \label{tab:gensup}}
   \end{center}

One can show that under supersymmetry transformations these component fields transform linearly into each other, thus we say that superfields (with the differential form of the supersymmetry generators) are {\it representations} of the supersymmetry (super-Poincar\'e) group just as ordinary quantum fields are representations of the Poincaré group, albeit {\it highly reducible} representations!\footnote{Indeed, they are linear representations since a sum of superfields is a superfield, and the differential supersymmetry operators act linearly.}

@@

%Note that the projection operators that we defined in Section~\ref{sec:covder}, $\pi_\pm$, project out left-/right-handed superfields, respectively, because:
%\[\bar{D}_{\dot{A}}\pi_+\Phi = D_A \pi_- \Phi^\dagger = 0.\]
%This is analogous to the familiar properties of $P_{L/R} = \frac{1}{2}(1\mp \gamma_5)$ in field theory.

%%%
\subsection{Scalar superfields}
%%%
What is the connection of the scalar superfields to the $j=0$ irreducible representation? To see this we use a cute trick:\footnote{Here cute is used in the widest sense.} Change to the variable $y^\mu \equiv x^\mu + i\theta\sigma^\mu \bar{\theta}$. Then the covariant derivatives simplify to
\begin{eqnarray}
D_A &=& \partial_A + 2i\sigma^\mu_{A\dot{A}}\bar{\theta}^{\dot{A}}\frac{\partial}{\partial y^\mu},\\
\bar{D}_{\dot{A}} &=& -\partial_{\dot{A}}.
\end{eqnarray}
This means that a field fulfilling $\bar{D}_{\dot{A}} \Phi = 0$ in the new set of coordinates must be independent of the $\bar{\theta}$ coordinates. Thus we can write this field as:
\begin{equation}
\Phi(y, \theta) = A(y) + \sqrt{2}\theta\psi(y) + \theta\theta F(y),
\label{eq:leftscalarsuperfield_y}
\end{equation}
and looking at the much restricted component field content we get the result in Table~\ref{tab:lscsup}.
\begin{center}
   \begin{tabular}{c |l| c} 
   \noalign{\smallskip}\hline\noalign{\smallskip}
   {\bf Component field} & {\bf Type} & {\bf d.o.f.} \\
   \noalign{\smallskip}\hline\noalign{\smallskip}
   $A(x)$, $F(x)$ & Complex scalar & 2\\
   $\psi_A(x)$ & Left-handed Weyl spinor & 4\\
   \noalign{\smallskip}\hline\noalign{\smallskip}
    \end{tabular}
   \captionof{table}{Fields contained in a left-handed scalar superfield. \label{tab:lscsup}}
   \end{center}

>>>>

If we now want to see how a Lorentz transformation $\Lambda$ acts for example on a scalar function $F(x)$  we can write $F(x)=\exp(ix^\mu P_\mu)F(0)$. This means that the transformation is essentially captured as $x'$ in $\Lambda\exp(ix^\mu P_\mu)= \exp(ix'^\mu P_\mu)$. Now, from the above we have
\[ \Lambda\exp(ix^\mu P_\mu)=\Lambda T(x)=T(\Lambda x) \Lambda, \]
and since the Lorentz transformation does nothing to a scalar coordinate independent quantity such as $F(0)$, we have $x'^\mu=\Lambda^\mu_{~\nu} x^\nu$, and the scalar function transforms the way we are used to under Lorentz transformations, namely $\Lambda F(x)= F(x')$. This argument can easily be extended to vector fields $A_\mu(x)$ and higher rank tensors, for example
\[ \Lambda A^\nu(x)= \Lambda^\mu_{~\nu} A^\nu(x'). \]
 The way we have defined four-vectors have built the Lorentz transformations of Special Relativity into our equations.

@@

In order for the exponential map to make sense the parameters $\theta$ need to anti-commute just like the $Q$s so that the contractions $\theta^{A} Q_A$ and $\bar{\theta}_{\dot{A}}\bar{Q}^{\dot{A}}$ follow ordinary commutation rules. Otherwise the commutation properties of the exponential map would be different order by order.\footnote{We might already see how this can be useful: if we consistently use $\theta^AQ_A$ and $\bar{\theta}_{\dot{A}}\bar{Q}^{\dot{A}}$ instead of only $Q_A$ and $\bar{Q}^{\dot{A}}$ in Eqs.~(\ref{eq:QPweyl})--(\ref{eq:QQbarweyl}) we can actually rewrite the superalgebra as an ordinary Lie algebra, but with Grassman elements, because of these commutation properties.}
 As physicists we also want to know the dimensions of our new parameters. To do this we first look at Eq.~(\ref{eq:QQbarweyl}):
\[\{Q_A, \bar{Q}_{\dot{B}}\} = 2\sigma^{\mu}_{A\dot{B}}P_\mu,\]
where we know that $P_\mu$ has mass dimension $[P_\mu] = M$. This means that $[Q^2] = M$ and $[Q]=M^{1/2}$. In the exponential, all terms must have mass dimension zero to make sense. This means that $[\theta Q] = 0$, and therefore $[\theta] = M^{-1/2}$.

We now want to find the effect of supersymmetry transformations (transformations by the super-Poincaré group) on the superspace coordinates, and we begin by noting that any $SP$ transformation can effectively be written in the following way without the boosts and rotations of the Lorentz group:
\[g_0(a,\alpha) = \exp[ia^\mu P_\mu + i\alpha^AQ_A +i\bar{\alpha}_{\dot{A}}\bar{Q}^{\dot{A}}],\]
effectively setting $\omega_{\rho\nu}=0$, because we can again show that\footnote{Fortunately we are not going to do this because it is messy, but it can be done using the algebra of the group and the series expansion of the exponential function. Note, however, that the proof rests on the $P$s and $Q$s forming a closed set, which we saw in the algebra Eqs.~(\ref{eq:QPweyl})--(\ref{eq:QQbarweyl}).}
\begin{equation}
\exp\left[\frac{i}{2}\omega_{\rho\nu}M^{\rho\nu}\right]g_0(a,\alpha) = g_0(\Lambda a,S(\Lambda)\alpha)\exp\left[\frac{i}{2}\omega_{\rho\nu}M^{\rho\nu}\right],
\end{equation}
{\it i.e.}\ that all that a Lorentz boost does is to transform spacetime coordinates by $\Lambda$ and Weyl spinors by $S(\Lambda)$, which is the spinor representation of $\Lambda$ ($SL(2,\mathbb C)$). Thus, in more colloquial terms, for the supersymmetry transformation it does not matter which reference frame we are working in, we know how the transformation changes between the frames, given by  $\Lambda a$  and $S(\Lambda)\alpha$.

@@

Now we take a closer look at the commutator:\footnote{Using that $P_\mu$ commutes with all the other generators present, as well as $[\theta^A Q_A, \xi^B Q_B] = -\theta^A\xi^B\{Q_A, Q_B\} = 0$, and similarly for $\bar{Q}^{\dot{B}}$.}

@@

As a crucial by-product we can now write down a differential representation for the supersymmetry generators by applying the standard expression for the generators $X_i$ of a Lie algebra, given the composition functions $f_\pi$:
\[ iX_j = \frac{\partial f_\pi}{\partial a_j}\frac{\partial}{\partial z_\pi},\]
which gives us:
\begin{eqnarray}
iP_\mu &=& \partial_\mu \label{eq:diffrepP},\\
iQ_A &=& -i(\sigma^\mu\bar{\theta})_A\partial_\mu +\partial_A,\\
i\bar{Q}^{\dot{A}} &=& -i(\bar{\sigma}^\mu \theta)^{\dot{A}}\partial_\mu +\partial^{\dot{A}}.
\label{eq:diffrepQbar}
\end{eqnarray}
The interested reader can now use these expressions to check the (anti-)commutation relations for the supercharges in Eqs.~(\ref{eq:QQweyl}) and (\ref{eq:QQbarweyl}).

%%%%%%%%%%%%%%%
\section{Superspace calculus}
\label{sec:calc}
%%%%%%%%%%%%%%%
It should be clear from the following section that we need to know something about the calculus of anti-commuting Grassmann numbers in order to make sense of differentiation (and integration) with respect to them. In this section we will briefly discuss their most important properties, focusing on the coordinates of superspace.

As Grassmann numbers the superspace coordinates obey the following commutation rules:
\[\{\theta_A, \theta_B\} = \{\theta_A, \bar{\theta}_{\dot{B}}\} = \{ \bar{\theta}_{\dot{A}}, \theta_B\} = \{\bar{\theta}_{\dot{A}}, \bar{\theta}_{\dot{B}}\} =0.\]
From this we get the relationships:\footnote{There is no summation implied in the first two lines, only a repetition of the same superspace coordinate. These are of course the same relations we already used for the Weyl spinors.}
\begin{eqnarray}
\theta_A^2 &=& \theta_A \theta_A = -\theta_A \theta_A = 0, \label{eq:thetasq}\\
\bar{\theta}_{\dot{A}}^2 &=& \bar{\theta}_{\dot{A}}\bar{\theta}_{\dot{A}} = -\bar{\theta}_{\dot{A}}\bar{\theta}_{\dot{A}} = 0, \\
\theta^2 &\equiv& \theta\theta \equiv \theta^A\theta_A = -2\theta_1\theta_2,\\
\bar{\theta}^2 &\equiv& \bar{\theta}\bar{\theta} \equiv \bar{\theta}_{\dot{A}}\bar{\theta}^{\dot{A}} = 2\bar{\theta}^{\dot{1}}\bar{\theta}^{\dot{2}}.
\end{eqnarray}
Notice that if we have a function $f$ of a Grassman number, say $\theta_A$, then the all-order expansion of that function in terms of $\theta_A$, is
\begin{equation}
f(\theta_A) = a_0 + a_1 \theta_A,\label{eq:fexp}
\end{equation}
as there are simply no more terms because of (\ref{eq:thetasq}).

We now need to define differentiation and integration on these numbers in order to create a calculus for them.\footnote{These definitions have no infinitesimal interpretations, nor is there any separate notion of definite integrals.}
\df{We define differentiation in superspace  by:
\[\partial_A \theta^B \equiv \frac{\partial}{\partial \theta^A} \theta^B \equiv \delta_A{}^B,\]
with a product rule
\begin{eqnarray}
\partial_A(\theta^{B_1} \theta^{B_2}\theta^{B_3}\ldots\theta^{B_n} ) &\equiv& (\partial_A\theta^{B_1}) \theta^{B_2}\theta^{B_3}\ldots\theta^{B_n}\nonumber\\
&&- \theta^{B_1}(\partial_A\theta^{B_2})\theta^{B_3}\ldots\theta^{B_n}\nonumber\\
 && +\ldots+(-1)^{n-1}\theta^{B_1}\theta^{B_2}\ldots(\partial_A\theta^{B_n}).
 \end{eqnarray}}
 This implies that the differential operator $\partial_A$ is itself a Grassmann number and anti-commutes. We can show that the indices of these operators can be raised and lowered with the $\epsilon$ in Eqs.~(\ref{eq:epsilonAB}) and (\ref{eq:epsilonAdotBdot}).

\df{The integral of a function $f$ of a superspace coordinate $\theta_A$ is defined as a functional $I[f]$
\[ I[f]=\int d\theta_A \, f(\theta_A), \]
which evaluates to a {\bf $\mathbf c$-number} (number in $\mathbb C$). The evaluation is defined by the relations
 \[\int d\theta_A \equiv 0,\quad \int d\theta_A \, \theta_A \equiv 1,\] 
and similarly for $\bar\theta_{\dot A}$, and we demand linearity:
\[\int d\theta_A[af(\theta_A) + bg(\theta_A)] \equiv a\int d\theta_A f(\theta_A) + b\int d\theta_A g(\theta_A).\]
In these definitions there is no implied summation over the index $A$.}

This integral definition has a surprising property. If we take the integral of (\ref{eq:fexp}) we get:
\[\int d\theta_A f(\theta_A) = a_1 = \partial^A f(\theta_A),\]
meaning that differentiation and integration has the same effect on functions of Grassmann numbers.

To integrate over multiple Grassmann numbers we define volume elements as
\begin{eqnarray*}
d^2\theta &\equiv& -\frac{1}{4}d\theta^Ad\theta_A,\\
d^2\bar{\theta} &\equiv& -\frac{1}{4}d\bar{\theta}_{\dot{A}}d\bar{\theta}^{\dot{A}},\\
d^4\theta &\equiv& d^2\theta d^2\bar{\theta},
\end{eqnarray*}
and we demand that the integral operators anti-commute, just as the differential operators
\[ \{\int d\theta_A,\int d\theta_B\}=\{\int d\theta_A,\theta_B\}=0.\]
This specific volume element definition is made to normalise the following integrals
\begin{eqnarray*}
\int d^2\theta\text{ }\theta\theta &=& 1,\\
\int d^2\bar{\theta}\text{ }\bar{\theta} \bar{\theta} &=& 1,\\
\int d^4 \theta \text{ }(\theta\theta)(\bar{\theta} \bar{\theta}) &=& 1.
\end{eqnarray*}

@@

%%%%%%%%%%%%%%%
\section{Covariant derivatives}
\label{sec:covder}
%%%%%%%%%%%%%%%
Similar to the properties of covariant derivatives for gauge transformations in gauge theories, it would be nice to have a derivative that is invariant under supersymmetry transformations, {\it i.e.}\ commutes with the supersymmetry generators. Obviously $P_\mu = -i\partial_\mu$ does this, but more general covariant derivatives can be made.
\df{The following {\bf covariant derivatives} commute with supersymmetry transformations:
\begin{eqnarray}
D_A &\equiv& \partial_A + i(\sigma^\mu\bar{\theta})_A\partial_\mu ,\\
\bar{D}_{\dot{A}} &\equiv& -\partial_{\dot{A}}-i(\theta\sigma^\mu)_{\dot{A}}\partial_\mu.
\end{eqnarray}}

@@

From the covariant derivatives we can also construct  a set of three projection operators.
\df{The operators
\begin{eqnarray}
\pi_+ &\equiv& -\frac{1}{16\Box} \bar{D}^2D^2,\\
\pi_- &\equiv& -\frac{1}{16\Box} D^2\bar{D}^2,\\
\pi_T &\equiv& \frac{1}{8\Box} \bar{D}_{\dot{A}}D^2\bar{D}^{\dot{A}},
\end{eqnarray}
with $\Box\equiv\partial_\mu\partial^\mu$, are orthogonal projection operators, {\it i.e.}\ they fulfil:
\begin{eqnarray}
\pi_{\pm,T}^2 &=&\pi_{\pm, T}, \\
\pi_+\pi_- &=& \pi_+\pi_T = \pi_-\pi_T= 0,\\
\pi_+ + \pi_- + \pi_T &=& 1.
\end{eqnarray}
}

@@

We can expand any such superfield $\Phi(x, \theta, \bar{\theta})$  as a power series in $\theta$ and $\bar{\theta}$. For a superfield without explicit spinor indices this gives in general,
%\footnote{Equation (\ref{eq:gen_sup}) can be shown to be closed under supersymmetry transformations, meaning that a superfield transforms into another superfield under the transformations of the previous section.}
\begin{eqnarray}
\Phi(x, \theta, \bar{\theta}) &=& f(x) + \theta^A\phi_A(x) + \bar{\theta}_{\dot{A}}\bar{\chi}^{\dot{A}}(x) + \theta\theta m(x) + \bar{\theta}\bar{\theta}n(x) \nonumber\\ 
&& + \theta \sigma^\mu \bar{\theta}V_\mu(x) + \theta \theta \bar{\theta}_{\dot{A}}\bar{\lambda}^{\dot{A}}(x) +\bar{\theta}\bar{\theta}\theta^A\psi_A(x) + \theta\theta\bar{\theta}\bar{\theta}d(x),\label{eq:gen_sup}
\end{eqnarray} 
where the functions of space-time coordinates $x$ are called the {\bf component fields}. Any superfield without explicit spinor indices, such as the one above, commutes with any other superfield, because all the Grassmann numbers appear in contracted pairs.

The properties of the component fields can be deduced from the requirement that $\Phi$ must be an (operator valued) Lorentz scalar or pseudoscalar. These are shown in Table~\ref{tab:gensup} along with the corresponding degrees of freedom each field has.
\begin{center}
   \begin{tabular}{c |l| c} 
   \noalign{\smallskip}\hline\noalign{\smallskip}
   {\bf Component field} & {\bf Type} & {\bf d.o.f.} \\
   \noalign{\smallskip}\hline\noalign{\smallskip}
   $f(x)$, $m(x)$, $n(x)$ & Complex (pseudo) scalar & 2\\
   $\psi_A(x)$, $\phi_A(x)$ & Left-handed Weyl spinor & 4\\
   $\bar{\chi}^{\dot{A}}(x)$, $\bar{\lambda}^{\dot{A}}(x)$ &Right-handed Weyl spinor& 4\\
   $V_\mu(x)$ & Lorentz 4-vector (complex) & 8\\
   $d(x)$ & Complex scalar & 2 \\
   \noalign{\smallskip}\hline\noalign{\smallskip}
    \end{tabular}
   \captionof{table}{Component field content of a general superfield. \label{tab:gensup}}
   \end{center}

One can show that under supersymmetry transformations these component fields transform linearly into each other, thus we say that superfields (with the differential form of the supersymmetry generators) are {\it representations} of the super-Poincar\'e group -- in the sense of being states in the representation space -- just as ordinary quantum fields are representations of the Poincaré group, albeit {\it highly reducible} representations!\footnote{Indeed, they are linear representations since a sum of superfields is a superfield, and the differential supersymmetry operators act linearly.}

@@

Note that the projection operators that we defined in Section~\ref{sec:covder}, $\pi_\pm$, project out left-/right-handed superfields, respectively,  from the general superfield, because:
\[\bar{D}_{\dot{A}}\pi_+\Phi = D_A \pi_- \Phi^\dagger = 0, \]
which follows from using Eq.~(\ref{eq:D3}). This is analogous to the properties of $P_{L/R} = \frac{1}{2}(1\mp \gamma_5)$ that we saw in Sec.~\ref{sec:Dirac_spinors}.

%%%
\subsection{Scalar superfields}
%%%
What is the connection between the scalar superfields and the $j=0$ irreducible representation? To see this we use a cute trick:\footnote{Here cute is used in the widest sense.} Change to the variable $y^\mu \equiv x^\mu + i\theta\sigma^\mu \bar{\theta}$. Then the covariant derivatives simplify to
\begin{eqnarray}
D_A &=& \partial_A + 2i\sigma^\mu_{A\dot{A}}\bar{\theta}^{\dot{A}}\frac{\partial}{\partial y^\mu},\\
\bar{D}_{\dot{A}} &=& -\partial_{\dot{A}}.
\end{eqnarray}
This means that a field fulfilling $\bar{D}_{\dot{A}} \Phi = 0$ in the new set of coordinates must be independent of the $\bar{\theta}$ coordinates. Thus we can write this field as:
\begin{equation}
\Phi(y, \theta) = A(y) + \sqrt{2}\theta\psi(y) + \theta\theta F(y),
\label{eq:leftscalarsuperfield_y}
\end{equation}
and looking at the much restricted component field content we get the result in Table~\ref{tab:lscsup}.
\begin{center}
   \begin{tabular}{c |l| c} 
   \noalign{\smallskip}\hline\noalign{\smallskip}
   {\bf Component field} & {\bf Type} & {\bf d.o.f.} \\
   \noalign{\smallskip}\hline\noalign{\smallskip}
   $A(x)$, $F(x)$ & Complex scalar & 2\\
   $\psi_A(x)$ & Left-handed Weyl spinor & 4\\
   \noalign{\smallskip}\hline\noalign{\smallskip}
    \end{tabular}
   \captionof{table}{Component fields contained in a left-handed scalar superfield. \label{tab:lscsup}}
   \end{center}
